Draft

### 2017-08-25 Thesis/Draft.tex
Add Introduction

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

@@

{
\hypersetup{linkcolor=black}
\setcounter{tocdepth}{3}
\tableofcontents
}
\section{Thresholding Bandit Problem}\label{thresholding-bandit-problem}

The \emph{Thresholding Bandit Problem} described in Locatelli et al.
(2016) can be considered a variant of a variant. It can be framed into
the wider literature of \emph{Pure Exploration} multi-armed bandit
problems. In particular, it shares characteristics with the
\emph{Top-\(m\)} problem. This problem is concerned with finding the
\(m\) best arms as described by the means of their corresponding
distributions. This in turn is similar to the \emph{combinatorial
bandit} problem, which also aims at finding the \(m\) best arms.
However, it is able to pull several arms at once: Think of an online
shop that shows five recommended products on a product detail page.
These five recommended products might each be represented by an arm, and
we look for the products with the largest mean conversion rate. The
thresholding bandit problem we discuss here, however, is concerned with
pulling a single arm at a time. And so a more appropriate situation is
that of a website presenting a banner. Again, think of an online shop
trying to promote a certain category. The content team came up with a
number of different designs for the banner, and it's not clear how many
click-throughs they will gather.

@@

In any case, the problem boils down to the following. As standard in
multi-armed bandit problems, we have \(K\) arms
\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
collect feedback in form of the random variable \(X_{k,t}\) which is
distributed according to the arm's distribution \(\nu_k\). In general,
we are concerned with estimating for each arm \(i\) the mean \(\mu_i\)
of its distribution \(\nu_i\). In contrast to most bandit problems,
however, we do not directly compare arms with each other by comparing
their means. That would for example be the case for pure exploration
bandits, where it is necessary to compare the arms because one aims to
find the best one relative to the others. In the case of the
thresholding bandit, however, we compare each arm's mean \(\mu_i\)
individually against the threshold \(\tau \in \mathbb{R}\) which is
known and fixed before the experiment. One might compare this to a pure
exploration bandit in which the mean of the best arm is known upfront.
We will see later that this fact leads to advantages in the design of
algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow an
\(R\)-sub-Gaussian distribution. Under this assumption, the authors are
able to proof a general lower bound as well as an algorithm with a
matching upper bound. Both hinge upon the \emph{complexity} of a given
problem. Since bandit problems can differ in the number of the arms
\(K\) and the means of each arm, some pose easier identification
problems than others. Indeed, in the thresholding problem, the
difficulty of the problem naturally depends on how close (the means of
the) distributions are to the fixed threshold. Intuitively, the closer a
mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it will
be to distinguish the two successfully based on samples from the
distribution \(\nu_i\). For the case of the sub-Gaussian distributions,
a natural measure of this distance is given by simply
\(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
\(2\epsilon\) interval around the threshold \(\tau\) in which we allow
ourselves to make a mistake at no cost.

If we extend this idea to the set of arms \(i \in \{1,...,K\}\) of a
given bandit problem, a natural measure of the overall diffulty of the
problem, or the problem's complexity, might be given by
\(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
adding additional arms leads to an increase in complexity (since we need
to sample more of them), just as smaller \(\Delta_i\) will increase the
complexity as arms become harder to classify. (WHERE DOES THIS
COMPLEXITY ORIGINALLY COME FROM?)

@@

Another characteristic uniquely identifying bandit problems is the
regret measure that we aim to optimize. As explained during the
introduction, multi-armed bandits traditionally optimize cumulative
regret. The notion of regret considered in the thresholding bandit,
however, is more akin to the simple regret in pure exploration bandits
or the error probability in sequential hypothesis testing. Indeed, one
can most easily describe the regret in the thresholding case as the
probability of making a misclassification of any arm. Or, more
rigorously, let us define the set of all arms with mean larger than the
threshold,
\(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
Consequently,
\(\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}\). At the end
of the sampling rule/procedure (!!we have not mentioned yet the fact
that we're in the fixed budget case!!), we demand that any algorithm
returns the two corresponding \emph{estimated} sets:
\(\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}\),
as well as
\(\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}\).
We simply demand an answer to the question which arms have means above
the threshold \(/tau\), and which arms lie below \(\tau\). Let \(T\) be
the overall number of samples the algorithm is allowed to pull. We
define the loss as
\(\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}\).
That is, we compare the return set with the true set and collect a loss
of 1 if any arm with a true mean outside the \(2\epsilon\) interval
around \(\tau\) was misclassified. It is important to realize that arms
with means inside the \(2 \epsilon\) interval may be misclassified
without it affecting the loss. These arms are considered close enough to
the threshold that we do not care whether they lie above or below.

@@

From there, it is natural to define the expected regret/loss as
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))\).
This, of course, is the mentioned probability of making a mistake.

ADD REMARK ON WHAT THIS IMPLIES WITH REGARD TO THE MEANS

@@

@@

From the general setup, we already know how the algorithm will end.
After it has drawn \(T\) samples, the algorithm makes its decision of
which arms to include in the return sets solely on basis of the
empirical means \(\hat{\mu}_i(T)\) estimated based on the samples drawn
until time \(T\). Furthermore, the threshold and interval around the
threshold were fixed upfront and serve as argument to the algorithm:
\((\tau, \epsilon)\). For a given arm \(i\) and a given time \(t\), we
let \(T_i(t)\) represent the number of samples drawn from arm \(i\)
until time \(t\) (including). Consequently, the empirical mean of arm
\(i\) at time \(t\) is given by
\(\mu_i = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
arm is pulled for the \(s\)-th time.

@@

\textbf{Remark}: Obviously, the APT algorithm tends to pull arms more
often with corresponding mean close to the threshold and interval (small
\(\hat{\Delta}_i(t))\). This makes sure that more evidence is gathered
on arms which appear to be inherently difficult to classify based on the
samples collected until time \(T_i(t)\), as these arms stifle the
confidence the most. That is, until we have collected enough evidence to
make a confident classification even if the mean is truly close to the
threshold. In that case, \(\sqrt{T_i(t)}\) will raise \(B_i(t+1)\).
Consequently, other arms farther away from the threshold will be sampled
again. In this way, the algorithm tries to distribute the budget \(T\)
over all arms so as to define a sampling rule optimizing the confidence
of the final decision. This is Glivenko-Cantelli and the CLT making sure
\(B_i(t+1)\) is not degenerate. (?)

@@

Yet another idea, again mentioned in Locatelli et al. (2016) is to show
bounds based on the Kullback-Leibler divergence of the specific
distribution directly. While the approximation through the Gaussian
Kullback-Leibler divergence in the lower bound proof is convenient and
leads to the simple APT algorithm, it might not stay appropriate for
distributions whose Kullback-Leibler divergence tends to differ from the
Gaussian. This, for example, is the case for Bernoulli distributions at
very small parameters \(\mu\). By looking at the graphical examples
below it becomes obvious that the Kullback-Leibler divergence of
Bernoullis starts to lose any similarity to the plain quadratic
approximation. The second graph then shows that the actual
Kullback-Leibler divergence of Bernoullis also has lost any symmetry
over this range of parameter values. Given that Bernoulli distributions
with very small parameter values arise naturally in many applications in
website optimization and advertising click-through modeling, there is a
need to tackle this problem.

Refer also to page 6 in Kaufmann et al. (2016): ``This
information-theoretic lower bound permits to interpret the quantity
\(H(\nu)\) defined in (2) as a subgaussian approximation''.

And so a potential approach can be to use the Kullback-Leibler
divergence as measure similar to the methods proposed in Kaufmann et al.
(2015). They proposed Kullback-Leibler based approaches for the pure
exploration bandit setting, which we will describe in chapter 2. Then,
in chapter 3, we will come back to the problem of using the
Kullback-Leibler divergence in the thresholding bandit setting.

@@

\subsection{Upper Bound: Theorem and
Proof}\label{upper-bound-theorem-and-proof}

@@

\emph{Proof of Theorem \ref{theorem:LocatelliTheorem4}:} To prove above
theorem, we first define a favorable event \(\xi\) on which we hope to
make a loss with only a small probability. Indeed, it is the event for
which we want to upper bound the expected loss. As we want to find an
upper bound for the expected loss of the APT algorithm, the event
corresponds to the decision made by it. Given that the APT algorithm's
sampling rule and final decision is based on the empirical mean of each
arm, it will have low expected regret, if it finds empirical mean
estimates \(\hat{\mu}_i(t) = \frac{1}{s} \sum_{t=1}^s X_{i,t}\) that are
close to the true means \(\mu_i\) of the arms. Then, we would expect
arms with \(\hat{\mu}_i(T) > \tau + \epsilon\) to be classified
correctly, and arms with \(\hat{\mu}_i(T) < \tau - \epsilon\) to be
rejected.

Indeed, we have
\(\mathbb{E}(\mathcal{L}(T)) = P(S_{\tau + \epsilon} \cap \hat{S}_\tau^C \neq \emptyset \lor S_{\tau-\epsilon}^C \cap \hat{S}_{\tau} \neq \emptyset)\).
But this just corresponds to
\(P(\{\exists i: ((\mu_i < \tau-\epsilon) \land(\hat{\mu}_i \geq \tau)) \lor ((\mu_i > \tau + \epsilon) \land (\hat{\mu}_i < \tau)))\).
Each of the two \((...)\lor(...)\) conditions corresponds to
\(| \hat{\mu}_i - \mu_i | \geq \epsilon\). It follows that the expected
loss can be rewritten as:
\(\mathbb{E}(\mathcal{L}(T)) = P(\exists i, \exists s: |\hat{\mu}_{i,s} - \mu_i | \geq \epsilon) = P(\xi^C)\).
This is exactly the probability of classifying at least one arm
incorrectly which results in a loss of size 1.

Thus we define as the favorable event as:

\begin{equation} 
\xi = \{\forall i, \forall s: | \hat{\mu}_{i,s} - \mu_i | \leq
\epsilon\} 
\end{equation}

Furthermore, if we write
\(\xi_{i,s} = \{ |\hat{\mu}_{i,s}-\mu_i | \leq \epsilon \}\), then the
following holds by a union bound.

\begin{equation} 
P(\xi) = P(\cap_i \cap_s \xi_{i,s}) = 1 - P(\cup_i \cup_s
\xi_{i,s}^C) \geq 1 - \sum_i \sum_s P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon)
\label{theorem2_prob_fav_event} 
\end{equation}

Furthermore, for any \(i \in \{1, \dots, K\}\), for any
\(s \in \{1, \dots, T(i)\}\), with \(X_{it}\) being the random sample
from the R-sub-Gaussian distribution \(v_i\) at time \(t\):

\begin{equation} 
P(| \hat{\mu}_{i,s} - \mu_i| \geq \epsilon) = P(| (\frac{1}{s}
\sum_{t=1}^{s} X_{it} - \mu_i) | \geq \epsilon) = P(| \sum_{t=1}^{s} (X_{it} -
\mu_i) | \geq s \epsilon) 
\end{equation}

where the latter can be bounded by a Hoeffding inequality:

\begin{equation} 
P(| \sum_{t=1}^{s} (X_{it} - \mu_i) | \geq s \epsilon) \leq
2\exp (-\frac{\epsilon^2 s}{2 R^2}) \label{theorem2_hoeffding} 
\end{equation}

The Hoeffding inequality as used here is as follows (compare chapter 2.4
in \href{http://www.stat.yale.edu/~pollard/Books/Mini/Basic.pdf}{David
Pollard (2015)}):

\begin{lemma}[Hoeffding's Inequality] \label{lemma:HoeffdingInequality}
Consider $X_1, \dots, X_T$ independent random variables from R-sub-Gaussian distributions $\nu_i$ with mean $\mu_i$. Then, for any $\epsilon > 0$,

>>>>

\usepackage[retainorgcmds]{IEEEtrantools}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{bbm}
\usepackage[lined,boxed]{algorithm2e}
\newtheorem{theorem}{Theorem}
\newtheorem{lemma}{Lemma}
\newcommand{\KL}{\,\text{KL}}
\newcommand{\der}{\,\text{d}}

@@

{
\hypersetup{linkcolor=black}
\setcounter{tocdepth}{2}
\tableofcontents
}
\newpage

``In general, we look for a new law by the following process: First we
guess it. Then we -- now don't laugh, that's really true. Then we
compute the consequences of the guess to see what, if this is right, if
this law that we guessed is right, to see what it would imply. And then
we compare the computation results to nature, or we say compare to
experiment or experience, compare it directly with observations to see
if it works. If it disagrees with experiment, it's wrong. In that simple
statement is the key to science. It doesn't make any difference how
beautiful your guess is, it doesn't make any difference how smart you
are, who made the guess, or what his name is. If it disagrees with
experiment, it's wrong. That's all there is to it.''

\begin{itemize}
\tightlist
\item
  Richard Feynman in \emph{Richard Feynman Messenger Lectures at Cornell
  University: The Character of Physical Law. Chapter 7, Seeking New
  Laws}.
\end{itemize}

\section{Abbreviations}\label{abbreviations}

Kullback-Leibler divergence between distributions \(\nu_i\) and
\(\nu_j\): \(\KL(\nu_i||\nu_j)\).

Binary relative entropy:
\(d(x,y) := x \log(x/y) + (1-x) \log((1-x)/(1-y))\), where
\(d(0,0) = d(1,1) = 0\).

Kullback-Leibler divergence for two Bernoulli distributions
parameterized by their means \(\mu_i\) and \(\mu_j\):
\(KL_{Ber}(\nu_i||\nu_j) = d(\mu_i, \mu_j)\).

\section{Introduction to Sequential Sampling and Multi-Armed
Bandits}\label{introduction-to-sequential-sampling-and-multi-armed-bandits}

The thesis at hand joins the ranks of a large literature concerned with
the general problem of sequential sampling. One is familiar with the
idea of ``batch sampling'', where the entire sample is gathered first
and analyzed only after the last sample has become available. However,
as noted in Chernoff (1958), many situations arise in which one would
like to gather feedback from samples as they are drawn so as to
influence the choice of the next sample. The two fundamental
characteristics of the latter sampling process are that it is sequential
and adaptive. Since observations are drawn in sequence, one has a chance
to observe the observations drawn so far in order to adapt the decision
of what sample one would like to observe next.

This makes sequential sampling especially relevant in situations where
there is a inherent cost to drawing an observation. The classical
example that of clinical trials in which a researcher tests two drugs on
patients to observe which one performs better. Not only is it difficult
to gather patients, but also one would like to adapt the sampling such
that as soon as possible more patients receive the better drug so that
more patients are cured. As noted in Cappé et al. (2013), this example
dates back to Thompson (1933, 1935). Such problems are known as
multi-armed bandit problems in which the sampling is adapted so as to
minimize the cumulative regret: In the case of the drug tests, one would
like to sample the two drugs in a way to find the best drug as soon as
possible and then to test this drug more and more often and more often
than the worse drug. This would lead to cumulatively more healthy
patients then when both drugs are tested uniformly and thus minimize the
regret from treating a patient with an ineffective drug.

Instead of drugs, can consider two or more unknown distributions (which
we call arms in the multi-armed bandit problem). These distributions
have different means, and one can draw samples sequentially from the
distributions in order to estimate their means. One would like to play
the distribution with the highest mean to minimize the cumulative regret
measure. How can we organize the sampling in order to achieve this goal?

While Gittins (1979) presents an Bayesian-optimal solution, the
Upper-Confidence Bound algorithms pioneered by Agrawal (1995) and Auer,
Cesa-Bianchi and Fischer (2002) lead to a blooming literature on
multi-armed bandit problems that has been picked up to solve modern
problems in website and advertising optimization, where advertisers try
to allocate their advertising optimally so as to reduce regret from
showing poorly converting advertisements. Several algorithms as the
KL-UCB algorithm based on Kullback-Leibler divergence upper confidence
intervals (Cappé et al., 2013) or the Bayes-UCB algorithm (Kaufmann et
al., 2012) have followed and been shown to be optimal as they reach the
lower bound introduced in Lai and Robbins (1985) and Burnetas and
Katehakis (1996).

These algorithms have in common that they compute after any sample an
index for each of the unknown distributions. This index is based solely
on the past (observed) data, and then used to pick the distribution from
which the next observation should be drawn. Using these indexes, the
algorithms can sequentially sample and adapt the future strategies to
observations as they are gathered.

Other algorithms based on indices can be used on related problems.
Instead of minimizing cumulative regret, it might be more interesting to
find the best arm, that is, the distribution with the largest mean, with
as few samples as possible and with confidence as large as possible.
This is particularly useful when there is not necessarily a cost from
initially picking a lower mean, but when drawing any sample is costly,
and one needs to explore the distributions as efficiently as possible.
The need for strategies other than uniform sampling arises: Do not
continue to sample distributions that we are confident about. As such,
the best arm identification problem is very similar to the problem faced
in Bayesian Optimization: Training large neural networks is costly in
terms of time and computation, and so the parameter space needs to be
explored with as few samples as possible. (Zhang et al., 2017; Brochu et
al., 2010).

The problem of best arm identification is very related to statistical
hypothesis testing as noted by Chernoff (1958) since in the end, one has
to make a decision about how the means of distributions relate to each
other. The main difference of course being that the sampling procedure
becomes integrated into the evaluation of the distributions. Given the
focus on exploration, the problem is usually described with a loss
function different from cumulative regret. Audibert et al. (2010)
introduce a soft measure called \emph{simple regret} based on which they
describe UCB policies. Other authors investigate hard, binary measures
that are equal to 1 when the best arm has not been identified (Russo,
2016; Garivier and Kaufmann, 2016).

The problem of best arm identification can readily be extended to the so
called Top-\(m\) problem of identifying the best \(m\) of \(K\) arms.

\begin{itemize}
\item
  Chernoff -\textgreater{} Sequential Sampling; as mentioned by Russo;
  Garivier and Kaufmann
\item
  Thompson
\item
  Optimality for Stochastic Cumulative Regret
\item
  UCB, KL-UCB, Thompson Sampling
\end{itemize}

-\textgreater{} Many variations: Infinite-armed, adversarial, dueling

\begin{itemize}
\item
  Best Arm Identification
\item
  Top-\(m\) Identification
\item
  Thresholding Bandit Problem
\item
  Maybe an example?
\end{itemize}

\section{Thresholding Bandit Problem}\label{thresholding-bandit-problem}

The \emph{Thresholding Bandit Problem} described in Locatelli et al.
(2016) can be considered a variant of a variant. It can be framed inside
of the wider literature of \emph{Pure Exploration} multi-armed bandit
problems. In particular, it shares characteristics with the
\emph{Top-\(m\)} problem. This problem is concerned with finding the
\(m\) best arms as described by the means of their corresponding
distributions. This in turn is similar to the \emph{combinatorial
bandit} problem, which also aims at finding the \(m\) best arms.
However, it is able to pull several arms at once: Think of an online
shop that shows five recommended products on a product detail page.
These five recommended products might each be represented by an arm, and
we look for the products with the largest mean conversion rate. The
thresholding bandit problem we discuss here, however, is concerned with
pulling a single arm at a time. And so a more appropriate situation is
that of a website presenting a banner. Again, think of an online shop
trying to promote a certain category. The content team came up with a
number of different designs for the banner, and it's not clear how many
click-throughs they will gather.

@@

In any case, the problem boils down to the following. As usual in
multi-armed bandit problems, we have \(K\) arms
\(\mathcal{A} = \{1, \dots K\}\). We can pull arm \(k\) at time \(t\) to
collect feedback in form of the random variable \(X_{k,t}\) which is
distributed according to the arm's distribution \(\nu_k\). In general,
we are concerned with estimating for each arm \(i\) the mean \(\mu_i\)
of its distribution \(\nu_i\). In contrast to most bandit problems,
however, we do not directly compare arms with each other by comparing
their means. That would for example be the case for pure exploration
bandits, where it is necessary to compare the arms because one aims to
find the best one relative to the others. In the case of the
thresholding bandit, however, we compare each arm's mean \(\mu_i\)
individually against the threshold \(\tau \in \mathbb{R}\) which is
known and fixed before the experiment. One might compare this to a pure
exploration bandit in which the mean of the best arm is known upfront.
We will see later that this fact leads to advantages in the design of
algorithms which are not as readily available in other bandit settings.

In Locatelli (2016), the arms' distributions are assumed to follow an
\(R\)-sub-Gaussian distribution. Under this assumption, the authors are
able to proof a general lower bound as well as an algorithm with a
matching upper bound. Both hinge upon the \emph{complexity} of a given
problem. Since bandit problems can differ in the number of the arms
\(K\) and the means of each arm, some pose easier identification
problems than others. Indeed, in the thresholding problem, the
difficulty of the problem naturally depends on how close (the means of
the) distributions are to the fixed threshold. Intuitively, the closer a
mean \(\mu_i\) is to the threshold \(\tau\), the more difficult it is to
distinguish the two successfully based on samples from the distribution
\(\nu_i\). A straightforward measure of this distance is given by
\(\Delta_i = |\tau - \mu_i| + \epsilon\), where \(\epsilon\) defines a
\(2\epsilon\) interval around the threshold \(\tau\) in which we allow
ourselves to make a mistake at no cost. In the case of sub-Gaussian
distributions, this distance is not only simple but can be interpreted
very naturally as we will come to understand later.

If we extend this idea to the set of arms \(i \in \{1,...,K\}\) in a
given bandit problem, a measure of the overall diffulty of the problem,
or the problem's complexity, might be given by
\(H = \sum_{i=1}^{K} \Delta_i^{-2}\). In particular, it shows that just
adding additional arms leads to an increase in complexity (since we need
a larger budget to sample each arm the same number of times as before).
Likewise, a smaller \(\Delta_i\) increases the complexity as arms become
harder to classify. Choosing the complexity measure in this way fits the
distance measure \(\Delta_i\) and turn out to be useful in the proof of
an upper bound for the APT algorithm presented in Locatelli et al.
(2016).

@@

Another characteristic uniquely identifying bandit problems is the
regret measure that we aim to optimize. As explained during the
introduction, multi-armed bandits traditionally optimize cumulative
regret. The notion of regret considered in the thresholding bandit,
however, is more akin to the simple regret in pure exploration bandits
or the error probability in sequential hypothesis testing. Indeed, one
can most easily describe the regret in the thresholding case as the
probability of misclassifying any arm. Or, more rigorously, define the
set of all arms with mean larger than the threshold,
\(\mathcal{S}_\tau = \{i \in \mathcal{A}: \mu_i \geq \tau\}\).
Consequently,
\(\mathcal{S}_\tau^C = \{i \in \mathcal{A}: \mu_i < \tau\}\). At the end
of the sampling rule/procedure (!!we have not mentioned yet the fact
that we're in the fixed budget case!!), we demand that any algorithm
returns the two corresponding \emph{estimated} sets:
\(\hat{\mathcal{S}}_{\tau} = \{i \in \mathcal{A}: \hat{\mu}_i \geq \tau\}\),
as well as
\(\hat{\mathcal{S}}_{\tau}^C = \{i \in \mathcal{A}: \hat{\mu}_i < \tau\}\).
We simply demand an answer to the question which arms have means above
the threshold \(/tau\), and which arms lie below \(\tau\). Let \(T\) be
the overall number of samples the algorithm is allowed to pull. We
define the loss as
\(\mathcal{L}(T) = \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset\}} \cdot \mathbbm{1}_{\{\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset\}}\).
That is, we compare the return set with the true set and collect a loss
of 1 if any arm with a true mean outside the \(2\epsilon\) interval
around \(\tau\) was misclassified. It is important to realize that arms
with means inside the \(2 \epsilon\) interval may be misclassified
without it affecting the loss. These arms are considered close enough to
the threshold that we do not care whether they lie above or below.

@@

Now, the expected regret/loss is defined as
\(\mathbb{E}[\mathcal{L}(T)] = \mathbb{P}((\hat{\mathcal{S}}_{\tau} \cap \mathcal{S}_{\tau-\epsilon}^C \neq \emptyset) \land (\hat{\mathcal{S}}_{\tau}^C \cap \mathcal{S}_{\tau+\epsilon} \neq \emptyset))\).
This, of course, is the mentioned probability of making a mistake.

@@

\IncMargin{1em}

\begin{algorithm}
\SetKwData{Left}{left}\SetKwData{This}{this}\SetKwData{Up}{up}
\SetKwFunction{Union}{Union}\SetKwFunction{FindCompress}{FindCompress}
\SetKwInOut{Input}{Input}\SetKwInOut{Output}{Output}
\Input{$\tau$, $\epsilon$}
\Output{$\hat{S}_{\tau} = \{k: \hat{\mu}_k(T) \geq \tau\}$}
\BlankLine
\emph{Pull each arm once}\;
\For{$t = K+1$ \KwTo $T$}{
  \emph{Pull arm $I_t = \arg \min_{k\leq K} B_k^{APT}(t) = \sqrt{T_k(t)} \sqrt{|\hat{\mu}_i(t) - \tau|+\epsilon}$}\;
  \emph{Observe reward $X \sim \nu_{I_t}$}\;
}
\caption{Anytime Parameter-free Thresholding Algorithm (Locatelli et al., 2016)}\label{algo_apt}
\end{algorithm}

\DecMargin{1em}

@@

From the general setup, we already know how the algorithm will end.
After it has drawn \(T\) samples, the algorithm makes a decision of
which arms to include in the return sets on basis of the empirical means
\(\hat{\mu}_i(T)\) estimated based on the samples drawn until time
\(T\). Furthermore, the threshold and interval around the threshold are
fixed upfront and serve as argument to the algorithm:
\((\tau, \epsilon)\). For a given arm \(i\) and a given time \(t\), we
let \(T_i(t)\) represent the number of samples drawn from arm \(i\)
until time \(t\) (including). Consequently, the empirical mean of arm
\(i\) at time \(t\) is given by
\(\hat{\mu}_i(t) = \frac{1}{T_i(t)} \sum_{s=1}^{T_i(t)} X_{i,s}\) where
\(X_{i,s}\) is the feedback sampled from distribution \(\nu_i\) when the
arm is pulled for the \(s\)-th time.

@@

\textbf{Remark}: Obviously, the APT algorithm tends to pull arms more
often with corresponding mean close to the threshold and interval (small
\(\hat{\Delta}_i(t))\). This makes sure that more evidence is gathered
on arms which appear to be inherently difficult to classify based on the
samples collected until time \(T_i(t)\), as these arms stifle the
confidence the most. That is, until we have collected enough evidence to
make a confident classification even if the mean is truly close to the
threshold. In that case, \(\sqrt{T_i(t)}\) will raise \(B_i(t+1)\).
Consequently, other arms farther away from the threshold will be sampled
again. In this way, the algorithm tries to distribute the budget \(T\)
over all arms so as to define a sampling rule optimizing the confidence
of the final decision.

@@

Yet another idea, again mentioned in Locatelli et al. (2016) is to show
bounds based on the Kullback-Leibler divergence of the specific
distribution directly. While the approximation through the Gaussian
Kullback-Leibler divergence in the lower bound proof is convenient and
leads to the simple APT algorithm, it might not stay appropriate for
distributions whose Kullback-Leibler divergence tends to differ from the
Gaussian. This, for example, is the case for Bernoulli distributions at
very small parameters \(\mu\). By looking at the graphical examples
below it becomes obvious that the Kullback-Leibler divergence between
Bernoulli distributions starts to lose any similarity to the quadratic
approximation. The second graph then shows that the actual
Kullback-Leibler divergence of Bernoulli distributions loses any
symmetry over this range of parameter values. Given that Bernoulli
distributions with very small parameter values arise naturally in many
applications in website optimization, advertising click-through
modeling, or anomaly detection in time series, there is a need to tackle
this problem.

Refer also to page 6 in Kaufmann et al. (2016): ``This
information-theoretic lower bound permits to interpret the quantity
\(H(\nu)\) defined in (2) as a subgaussian approximation''. In the case
of Normal distributions with known and equal mean, it holds that the
Kullback-Leibler divergence between \(\nu_i\) and \(\nu_j\),
parameterized by \(\mu_i\) and \(\mu_j\), can be written as

\[
\KL_{Normal}(\nu_i || \nu_j) = 2(\mu_i - \mu_j)^2.
\]

Writing \(\mu_j = \tau\) and \(\epsilon = 0\), we see that the APT
algorithm essentially measures the KL-divergence between two Normal
distributions. For two Bernoulli distributions \(\nu_i\) and \(\nu_j\),
parameterized by \(\mu_i\) and \(\mu_j=\tau\), we write

\[
\KL_{Ber}(\nu_i||\nu_j) = \mu_i \log(\frac{\mu_i}{\tau}) + (1-\mu_i) \log(\frac{1-\mu_i}{1-\tau})
\]

In the case of \(\tau = 0.5\), the latter KL-divergence is symmetric in
its first argument, and thus can be well approximated by Pinsker's
inequality:

\[
\KL_{Ber}(\nu_i||\nu_j) \geq 2(\mu_i - \tau)^2.
\]

This shows how the distance measure used in the APT algorithm, and
consequently the complexity \(H\), is a useful approximation of the
KL-divergence for sub-Gaussian distributions. However, this
approximation suffers as the distributions less and less similar to
Gaussian distributions. Thus similarly to how UCB algorithms in the
cumulative regret setting have been extended to KL-UCB algorithms
(compare Cappé et al., 2013), also the APT algorithm offers room for
improvement.

And so a potential approach can be to use the Kullback-Leibler
divergence as measure similar to the methods proposed in Kaufmann et al.
(2015). They proposed Kullback-Leibler based approaches for the pure
exploration bandit setting, which we will describe in chapter 2. Then,
in chapter 3, we will come back to the problem of using the
Kullback-Leibler divergence in the thresholding bandit setting. To
conclude chapter 1, we proof the lower bound and upper bound for the APT
algorithm as presented Theorem 1 and Theorem 2 in Locatelli et al.
(2016).

@@

\subsection{Upper Bound on Expected Loss of
APT}\label{upper-bound-on-expected-loss-of-apt}

@@

\emph{Proof of Theorem \ref{theorem:LocatelliTheorem4}:}

In order to upper bound the expected loss of the APT algorithm, we want
to find an event on which the algorithm would correctly seperate arms
from the threshold, that is, on the event a seperation condition holds.
We then want to show that with large probability, this \emph{favorable}
event does indeed hold. Consequently, the expected loss (probability of
an error) will correspond to the probability that the favorable event
does not hold after all as this leads the seperation condition to fail,
and the algorithm to classify at least one arm incorrectly.

While this is the general idea, we have to jump between seperation
condition, favorable event, and large probability.

\subsubsection{Separation Condition}\label{separation-condition}

As noted in Zhong et al. (2017), a simple requirement to correctly
classify arms at the final round is the following. For every arm
\(i \in \{1, ..., K\}\) at round \(T\),

\[
\hat{\mu}_{i,T_i(n)} \geq \mu_i - \frac{\mu_i - \tau + \epsilon}{2} \quad \text{if} \quad \mu_i \geq \tau
\] or

\[
\hat{\mu}_{i,T_i(n)} \leq \mu_i + \frac{\tau - \mu_i + \epsilon}{2} \quad \text{if} \quad \mu_i < \tau
\] Or simply in terms of the gap between the arm and the threshold as
used as index by the algorithm,

\[
| \hat{\mu}_{i, T_i(n)} - \mu_i | \leq \frac{|\mu_i - \tau| + \epsilon}{2} = \frac{\Delta_i}{2}.
\]

Intuitively, the conditions make sense as they ensure that the current
mean estimate is closer to the true mean than to the threshold.
Consequently, there is no possible arrangement left in which the
condition would hold, but the arm be classified incorrectly. Assuming
\(\mu_i < \tau\) and \(\epsilon = 0\), an incorrect classification would
require \(\mu_i < \tau \leq \hat{\mu_i}\). But then
\(| \hat{\mu}_{i, T_i(n)} - \mu_i | \geq |\mu_i - \tau|\), violating the
separation condition.

Thus, we need to show that in the very final round, this condition holds
for every arm \(i \in \{1,...,K\}\) with large probability. Or more
precisely, we need to derive a bound on the probability with which this
does not hold.

\subsubsection{The Favorable Event}\label{the-favorable-event}

The separation condition gives a good idea of what event we need to hold
in order to make a correct classification. The smaller the deviation of
the empirical mean from the population mean, the more difficult it is
for the classification to be wrong. Moreover, if the mean and empirical
mean are identical, then the classification is correct independent of
the threshold. And furthermore, the closer the mean and the threshold
are, the better the estimate must be for a correct classification.

Having to bound the absolute deviation of the sample mean from the
population mean is a very thankful operation. Define the favorable event
\(\xi\) as

\[
\xi = \Big\{\forall i \in \mathbb{A}, \forall s \in \{1,...,T\} : |\frac{1}{s} \sum_{t=1}^{s}X_{i,t} - \mu_i| \leq \sqrt{\frac{T \delta^2}{H s}} \Big\}.
\]

We want the probability that this favorable event occurs to be large,
that is, the probability that the deviation is small, such that the
separation condition holds with large probability. Indeed, we bound the
deviation for \emph{all} arms \(i \leq K\) and for \emph{every} round
\(s \leq T\). Using some Chernoff Hoeffding bounds, we are able to write

\[
\mathbb{P}(\xi) \geq 1 - 2(\log(T) +1)K \exp(-\frac{T\delta^2}{2R^2H})
\]

\subsubsection{\texorpdfstring{Need to Bound
\(T_i\)}{Need to Bound T\_i}}\label{need-to-bound-t_i}

We now have that with large probability, the favorable event holds. On
the favorable event, we have for every arm \(i\):

\[
| \hat{\mu}_i(t) - \mu_i| \leq \sqrt{\frac{T\delta^2}{HT_i(t)}}
\]
